# Bookdown basics {#basics}

In development.

## Subsections

Subsections can be created using pound signs (`#`):

```{r eval=FALSE}
# First-level header (only for the title)

## Second-level header

### Third-level header
```

The default use of the headers will produce numbers. This can be disabled using `{-}`after the header, e.g., `## Learning objectives {-}`.

## Cross-referencing

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro) using `\@ref(intro)`. If you do not manually label them, there will be automatic labels anyway, e.g., we can reference Chapter \@ref(citations) using the name of the chapter: `\@(citations)`.

## Code chunks

### Including or excluding chunks into the workshop script

## Figures and tables

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig) using `\@ref(fig:nice-fig)`. Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab) using `\@ref(tab:nice-tab)`.

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

## Citations

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015]. See Chapter \@ref(citations) for more information on how to make citations.
