--- 
title: "Template guide for the QCBS R Workshop Series"
author: "Québec Centre for Biodiversity Science"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [packages.bib, example.bib]
biblio-style: apalike
link-citations: yes
description: "This is the template that the books for all the workshops of the QCBS R Workshop Series will follow."
---

# Introduction {#intro}

This is a _template_ book written in **Markdown** using the **bookdown** package and based on '[A Minimal Book Example](https://github.com/rstudio/bookdown-demo)'as well a excerpts and concepts from '[bookdown: Authoring Books and Technical Documents with R Markdown](https://github.com/rstudio/bookdown)'.

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see http://rmarkdown.rstudio.com. When you click the Knit button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

New changes coming soon!

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
